---
title: "Multipanel Figures"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
# to install the patchwork package, run the line below
# remotes::install_github('thomasp85/patchwork')
library(patchwork)
library(cowplot)
library(ggsignif)
```

## Making single panels

We will start by making four plots, from four different datasets, all tagged with labels A-D.
Note the different themes used, and the control of figure width and height in the options for each chunk.


```{r panel1, fig.width= 6, fig.height= 4}
mtcars %>% 
  filter(cyl %in% c(4,6,8)) %>% 
  mutate(cyl = as.factor(cyl)) %>% 
  ggplot(aes(cyl, mpg)) +
  geom_boxplot() + labs(tag = 'A') +
  theme_linedraw() ->
p1
print(p1)
```

```{r panel2, fig.width= 3, fig.height= 2}
iris %>% 
  ggplot(aes(Species, Sepal.Length)) +
  geom_violin() +
  geom_jitter(alpha = 0.3, width = 0.2) + labs(tag = "B") +
  theme_cowplot() ->
p2
print(p2)
```

```{r panel3, fig.width= 2, fig.height= 4}
df <- data.frame(co2, month = 1:468) 
df %>% 
  ggplot(aes(month, co2)) +
  geom_line() +
  labs(x = 'month', y = 'CO2 concentration\nin ppm at Mauna Loa',
       caption = '1959 - 1997', tag = "C") +
  theme_dark() ->
p3
print(p3)
```


```{r panel4, fig.width= 5, fig.height= 3}
DNase %>% 
  ggplot(aes(conc, density)) +
  geom_jitter(alpha =0.4, width = 0.2) +
  geom_smooth() +
  labs(x = 'concentration of DNAse', y = 'Optical Density',
       caption = '11 replicates', tag = "D") +
  theme_half_open() ->
p4
print(p4)
```
## Now put them together

Let's start with patchwork, which is described here:
https://github.com/thomasp85/patchwork

### Self-arranging grid
```{r patches}
p1 + p2 + p3 + p4
```

### One figure on top, then 3 below
```{r patches2}
p1 / (p2 + p3 + p4)
```
### One row of figures
```{r patches3}
p1 + p2 + p3 + p4 + plot_layout(nrow =1)
```

### 3 on top, then one below
```{r patches4}
(p1 + p2 + p3) / p4
```

### One figure on top, two in middle row, then one below
```{r patches5}
p1 + (p2 + p3) + p4 + plot_layout(ncol = 1) & theme_bw()
```

## Now to cowplot
Cowplot uses a slightly different approach.
the cowplot package can be found at
https://cran.r-project.org/web/packages/cowplot/vignettes/introduction.html

Details here
https://cran.r-project.org/web/packages/cowplot/cowplot.pdf

### first remove tags, then 2 plots
```{r cowplot1}
# remove tags
p1 <- p1 + labs(tag = "")
p2 <- p2 + labs(tag = "")
p3 <- p3 + labs(tag = "")
p4 <- p4 + labs(tag = "")
plot_grid(p1, p2, labels = c('A', 'B'), label_size = 12)
```

### Now align axes to make it neater
```{r cowplot2}
plot_grid(p1, p2, labels = c('A', 'B'), label_size = 12, align = 'h')
```

### Single column
```{r cowplot3}
plot_grid(p1, p3, labels = c('A', 'B'), label_size = 12, align = 'v', ncol = 1)
```

### Control widths
```{r cowplot4}
plot_grid(p2, p4, labels = c('B', 'D'), label_size = 12, rel_widths = c(1, 0.5),
          align = 'h')
```

### Auto label with caps, control scale.
```{r cowplot5}
plot_grid(p1, p2, p3, p4, labels = c('AUTO'), scale = c(1, 0.9, 0.9, 0.6))
```